\vspace{-0.25em}\thetitle

### 2009-07-27 paper.tex
...

The properties of the model explain the structures seen in \Figure{svd}.
% This model is an ideal, and observed behaviors have noise introduced by sampling, imperfect adherence to the model, and outliers.
However, this is only one hypothesis that could fit the data.
Like any hypothesis, it must be tested.
The rest of this paper, aside from providing a practical application, serves as a hypothesis test:
we try to recover the matrices $W$ and $P$ from our imperfect observations of $Q$ and use the recovered model to predict real flow behaviors.
If the recovered model can make accurate predictions, this provides evidence that our model and hypothesis are largely accurate.

@@

>>>>

The properties of the model explain the structures seen in \Figure{svd}.
% This model is an ideal, and observed behaviors have noise introduced by sampling, imperfect adherence to the model, and outliers.
However, this is only one hypothesis that could fit the data.
Like any hypothesis, it must be tested.
The rest of this paper, aside from providing a practical application, serves as a hypothesis test:
we try to recover the matrices $W$ and $P$ from our noisy and imperfect observations of $Q$ and use the recovered model to predict real flow behaviors.
If the recovered model can make accurate predictions, this provides evidence that our model and hypothesis are valid.

@@

Our methodology for recovering the hypothesized linear structure of network traffic from trace samples uses a variety of cutting-edge and recently developed data-mining techniques.
To extract linear subspace structure, we use Ma~\emph{et~al.}'s 2007 algorithm based on lossy compression of data points~\cite{Ma07}.
